Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Conclusion

The GEM National Expert Survey however interesting and innovative for its extensive look into new sorts of data still allows for much improvement. It is essentially supposed to help control for the environmental determinants of entrepreneurship, which are here called the framework conditions. The major issue is not so much what it aims at revealing of the entrepreneurial context of each country but it has much more to do with methodology of data collection. Indeed, for each of these framework conditions, only four experts answered the survey, which makes the measure be very dependent on the individual respondent. This leads to highly variant data.

Regarding the D01 indicator we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect. Indeed, as we look at the way of teaching and education features, these are generally

>>>>

The GEM National Expert Survey however interesting and innovative for its extensive look into new sorts of data still allows for much improvement. It is essentially supposed to help control for the environmental determinants of entrepreneurship, which are here called the framework conditions. The major issue is not so much what it aims at revealing of the entrepreneurial context of each country but it has much more to do with methodology of data collection. Indeed, for each of these framework conditions, only four experts answered the survey, which makes the measure be very dependent on the individual respondent. This leads to highly variant data. Besides, the national teams hired by GEM Coordination Team were reported by GEM itself to manage time allocated for data collection rather poorly. That is, while they had five months at their disposal to approach and survey four experts for each framework condition, they happened on a regular basis to be in a hurry in July and therefore ended up relying on their personal connections to answer the surveys.

Regarding the D01 indicator that we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect. Indeed, as we look at the way of teaching and education features, these are generally culture related and as such should be much less fluctuant. At most, they should vary due to reforms being implemented at national, federal or state level, but that does not take place every year, rather every four or five years, sometimes only once a decade or even less frequently. Thus this yearly change is very unlikely to be a faithful figuration of how supportive of students' self-confidence teaching is like in a given country. On top of that, we purposely selected one item among the six used to characterised potential entrepreneurial education. That one item cannot be compensated by others in our study, which probably worsened the effect. The scale between 0 and 5 makes the assessment even more approximate. As a result of all these flaws combined leads to some variations of up to 1 point for some countries, like for Denmark for instance.

Now looking at GEM Adult Population Survey (APS), even if the data is directly collected by GEM from representatives samples of the population (around 2000 peole), once again we observe huge variation for indicators such as the perceived opportunities, which are unlikely to fluctuate that much in reality. That very indicator was used as a proxy for many potential control variables regarding economic outlook and other environmental determinants of entrepreneurship, and we do not expect the level of financing, the level of public programmes or the GDP growth for instance to vary that much from year to year. The subjective perception this indicator entails should have been compensated by the representativity of the sample and thus should not show so much variance. Once more, even if we are very doubtful about that data.

Last but not least is the scarcity of the data. For the perceived capabilities, perceived opportunities and fear of failure, there are already a few missing data but this gets much worse regarding the way of teaching. For that key explanatory variable, many countries have only data for have the years we were looking into, those who had the most data were at least missing three years, and three countries (Estonia, Luxembourg and Slovak Republic) had no data available at all.

Adding up all these limitations of the data we used, it does not come as a surprise that we could hardly get significant coefficients and could only observe general trends.

**Conclusion**

Education systems tend to be assessed in terms of numbers of students, ratios of teachers among other quantitative measures but what we tried to suggest here is that they could be looked at in quite a different way. As governments allocate public funds for education, they happen to make a long term investment, and, although this may not come as news, we intended here to propose a different rationale in doing so. Without denying the importance of all the classic determinants of entrepreneurship, we suggest that education systems could turn out to be one of those determinants that favour start up activites.

From the research we attempted to conduct here, due to poor quality and inconsistent data, we cannot ascertain our point but we still firmly believe there could be something happening out there and this should be looked into more. Now that would mean collecting the adequate amount of data and computing a new kind of indicators that are not yet available. This surely is a prospect for future research.
